---
title: "Accessing a pin on Connect from your local laptop"
format: html
author: "Lisa Anders"
date: "2025-03-27"
editor: source
---

## Purpose

This script pulls demo information from mtcars and pins it so the data set is usable by others, and from applications. This document is deployed to Connect and can be scheduled. 

Refer to the Connect documentation on pins here: <https://pins.rstudio.com/>

Refer to the pins documentation here: <https://docs.posit.co/connect/user/pins/>

```{r main, echo=FALSE, message=FALSE}
library(dplyr)
library(tidyverse)
library(stringr)
library(readr)
library(pins)
library(rsconnect)
library(usethis)

#Check our environment variables (for local use)
# usethis::edit_r_environ()
```

```{r}
#Pull data
summary(cars)
cars_data <- cars

#Pin data to board
board <- board_connect(auth = "envvar")
board %>% pin_write(cars_data, "cars_dataset", type = "rds")
```
## Conclusion

If you're reading this, it worked!

This document will be run on a schedule in the Connect environment, to provide updated data.  

## How to use the deployed pin 

Read it back with: 

```{r}
board <- board_connect(auth = "envvar")

cars_data_back <-board %>% pin_read("lisa.anders/cars_dataset")
```




