---
title: "Scheduling a pin to run on Connect"
format: html
author: "Lisa Anders"
date: "2025-03-27"
theme: pandoc
editor: source
---

```{r}
#| echo: false
library(gitlink)
gitlink::ribbon_css("https://github.com/leesahanders/dumb_pin_example.git", text="View on GitHub")
```

## Purpose

This script pulls demo information from mtcars and pins it so the data set is usable by others, and from applications. This document is deployed to Connect and can be scheduled. 

Refer to the Connect documentation on pins here: <https://pins.rstudio.com/>

Refer to the pins documentation here: <https://docs.posit.co/connect/user/pins/>

```{r main, echo=FALSE, message=FALSE}
library(dplyr)
library(tidyverse)
library(stringr)
library(readr)
library(pins)
library(rsconnect)
library(usethis)

#Check our environment variables (for local use)
# usethis::edit_r_environ()
```

```{r}
#Pull data - using a dummy "cars" dataset
summary(cars)
cars_data <- cars

board <- board_connect(auth = "envvar")

# Change this to your username
board %>% pin_write(cars_data, "lisa.anders/cars_dataset", type = "rds", force_identical_write = TRUE)
```
## Conclusion

If you're reading this, it worked!

This document will be run on a schedule in the Connect environment, to provide updated data.  

## How to use the deployed pin 

Read it back with: 

```{r}
board <- board_connect(auth = "envvar")

# Change this to your username
cars_data_back <-board %>% pin_read("lisa.anders/cars_dataset")

cars_data_back
```


## Session details: 

```{r}
library(roperators)
get_os()
Sys.info()['sysname']
R.Version()
system2("whoami", stdout = TRUE, stderr = TRUE)
system("cat /etc/*release")
```


<center> Built with [Quarto](http://quarto.org) </center>

